Flatiron cleaning

### 2021-10-20 Rmd/rdi analysis.Rmd
Update RDI and plots

```{r RDI calculation}
Frontline <- Treatment %>% 
  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
  #   group_by(patientid, chemotherapy_type) %>% 
  # mutate(linenumber_adj = dense_rank(linenumber_new)) %>%

  filter(chemotherapy_type == "Neoadjuvant" |
           (chemotherapy_type == "Adjuvant" &
              linenumber_adj == 1)) %>%

  mutate(relative_dose_intensity = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ amount/expected_dose,
    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
  )) %>%

  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("correct", "highly underdose", "underdose", "perfect", "higher dose", "overdose")))
```
<br>
<br>
<br>

@@

```{r echo=TRUE}
# RDI_grp = case_when(
#     mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
#     mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
#   ))
```
Start with plotting :

@@

<div class = "row">
<div class = "col-md-6">
```{r rdi plots, fig.height=10}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_boxplot()+
  # ylim(c(-.25, 3.5))+
  geom_jitter(shape=16)+
  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14)+
  facet_wrap(.~ drugname, ncol = 2)

<div class = "col-md-6">
```{r, fig.height=10}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  # geom_boxplot()+
  ylim(c(-.25, 3.5))+
  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal() +
  guides(color=FALSE)+
  facet_wrap(.~ drugname, ncol = 2)

# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
#   # filter(linenumber_new == "1") %>%
#   ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
#   geom_violin()+
#   ylim(c(-.25, 2.5))+
#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
#   theme_minimal(base_size = 14)+
#   facet_wrap(.~ drugname, ncol = 2)

# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
#   # filter(linenumber_new == "1") %>%
#   ggplot(aes(x= cycle_drugname, y= relative_dose_intensity))+
#   geom_violin(aes(color=relative_dose_intensity<0.85))+
#   ylim(c(-.25, 2.5))+
#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
#   theme_minimal()

@@

```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_violin()+
  # ylim(c(-.25, 2.5))+
  theme_minimal(base_size = 14)+
  facet_wrap(.~ drugname, ncol = 2, scales = "free_y")

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  ggplot(aes(x= drugname, fill = RDI_grp))+
  geom_bar(position = position_dodge())+
  theme_minimal(base_size = 14)+
  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
  coord_flip()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = chemotherapy_type))+
  geom_violin()+
  ylim(c(-.25, 3.5))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(drugname ~ RDI_grp, ncol = 2)

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= drugname, fill = RDI_grp))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  facet_wrap(.~ chemotherapy_type)+
  coord_flip()
```

```{r, fig.width=12, fig.height=20}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= raceeth, y= relative_dose_intensity#, alpha = relative_dose_intensity<0.85
             ))+
  geom_boxplot(aes(fill = drugname))+
  ylim(c(0, 2))+
  scale_colour_discrete()+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal(base_size = 14)+
  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")
```

As you will saw, we have a big spread of RDI (it is more than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI or being underdose or overdose

```{r echo=TRUE}
# (RDI_grp1 = case_when(
#     mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
#     mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
#     mean_RDI_per_chemotype_drug < 1                  ~ "correct",
#     mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
#     mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
#     mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
#   ))
```

```{r, fig.width=12}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  ggplot(aes(x= RDI_grp1, fill = drugname))+
  geom_bar(position = position_dodge())+
  theme_minimal(base_size = 10)+
  facet_wrap(drugname~ chemotherapy_type, ncol = 2, scales = "free")+
  coord_flip()
```

```{r, fig.width=12}
# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
#   ggplot(aes(x= drugname, fill = RDI_grp1))+
#   geom_bar(position = position_dodge())+
#   theme_minimal(base_size = 10)+
#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
#   coord_flip()
```

```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= drugname, fill = RDI_grp1))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 10)+
  coord_flip()+
  facet_wrap(.~ chemotherapy_type)
```
<br>
<br>

@@

<span style="color:green">**Platin**</span>  
```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels()

tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels()

tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels()

tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels()

tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              type = list(relative_dose_intensity ~ 'continuous'),
              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
  bold_labels()

tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
```

<span style="color:green">**Taxanes**</span>  
```{r Table summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels()

tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
  bold_labels()

tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels()

tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels()

tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(
              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
  bold_labels()

tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
```
<br>

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
Platin  
```{r Table4 summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

>>>>

```{r RDI calculation}
Frontline <- Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" |
           (chemotherapy_type == "Adjuvant" &
              linenumber_adj == 1)) %>%

  mutate(relative_dose_intensity = amount / expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "correct",
    mean_RDI_per_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "underdose",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug < 1                ~ "correct",
    mean_RDI_per_drug == 1                 ~ "perfect",
    mean_RDI_per_drug > 1 &
      mean_RDI_per_drug < 1.5              ~ "higher dose",
    mean_RDI_per_drug > 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("perfect", "correct", "higher dose", 
                                     "overdose", 
                                     "highly underdose", "underdose")))
```
<br>
<br>
<br>

@@

```{r echo=TRUE}
# RDI_grp = case_when(
#     mean_RDI_per_drug >= 0.85              ~ "correct",
#     mean_RDI_per_drug < 0.85               ~ "underdose"
#   ))
```
Start with plotting :

@@

<div class = "row">
<div class = "col-md-6">
```{r rdi plots, fig.height=10, fig.height=9}
Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= drugname))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(. ~ therapy)

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
  geom_boxplot()+
  # ylim(c(-.25, 3.5))+
  geom_jitter(shape=16)+
  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14)+
  facet_wrap(.~ drugname, ncol = 2)
```
</div>

<div class = "col-md-6">
```{r, fig.height=10, fig.height=9}
Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= drugname, fill= RDI_grp))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(. ~ therapy)

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
  # geom_boxplot()+
  ylim(c(-.25, 2))+
  geom_jitter(shape=16, aes(color=RDI_grp))+
  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14) +
  guides(color=FALSE)+
  facet_wrap(.~ drugname, ncol = 2)

# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   # filter(linenumber_new == "1") %>%
#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug, color = mean_RDI_per_drug<0.85))+
#   geom_violin()+
#   ylim(c(-.25, 2.5))+
#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
#   theme_minimal(base_size = 14)+
#   facet_wrap(.~ drugname, ncol = 2)

# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   # filter(linenumber_new == "1") %>%
#   ggplot(aes(x= cycle_drugname, y= mean_RDI_per_drug))+
#   geom_violin(aes(color=mean_RDI_per_drug<0.85))+
#   ylim(c(-.25, 2.5))+
#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
#   theme_minimal()

@@

```{r}
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
#   geom_violin()+
#   # ylim(c(-.25, 2.5))+
#   theme_minimal(base_size = 14)+
#   facet_wrap(.~ drugname, ncol = 2, scales = "free_y")

# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= drugname, fill = RDI_grp))+
#   geom_bar(position = position_dodge())+
#   theme_minimal(base_size = 14)+
#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
#   coord_flip()

# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   # filter(linenumber_new == "1") %>%
#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug, color = chemotherapy_type))+
#   geom_violin()+
#   ylim(c(-.25, 3.5))+
#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
#   theme_minimal(base_size = 14)+
#   coord_flip()+
#   facet_wrap(drugname ~ RDI_grp, ncol = 2)

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= drugname, fill = RDI_grp))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  facet_wrap(.~ chemotherapy_type)+
  coord_flip()
```

### By Population
```{r, fig.width=12, fig.height=20}
Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
             ))+
  geom_boxplot(aes(fill = drugname))+
  ylim(c(0, 2))+
  scale_colour_discrete()+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
  theme_minimal(base_size = 14)+
  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")
```

```{r ggridges, fig.width=16, fig.height=18}
library(ggridges)
Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(y=raceeth, x=mean_RDI_per_drug,  fill=raceeth
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 8)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+

  facet_wrap(therapy ~ drugname, ncol = 5, scales = "free_x")
```

@@

<span style="color:green">**Platin**</span>  
```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5),
          group_header = c("carboplatin/Neoadjuvant", 
                           "carboplatin/Adjuvant Upfront Surgery", 
                           "carboplatin/Adjuvant Upfront Chemo",
                           "cisplatin/Neoadjuvant", 
                           "cisplatin/Adjuvant Upfront Surgery", 
                           "cisplatin/Adjuvant Upfront Chemo"),
          quiet = TRUE)
```

<span style="color:green">**Taxanes**</span>  
```{r Table summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()
tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()
tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl7 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()
tbl8 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()
tbl9 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(#type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5, tbl9, tbl7, tbl8),
          group_header = c("paclitaxel/Neoadjuvant", 
                           "paclitaxel/Adjuvant Upfront Surgery", 
                           "paclitaxel/Adjuvant Upfront Chemo",
                           "PBB/Neoadjuvant", 
                           "PBB/Adjuvant Upfront Surgery", 
                           "PBB/Adjuvant Upfront Chemo",
                           "docetaxel/Neoadjuvant", 
                           "docetaxel/Adjuvant Upfront Surgery", 
                           "docetaxel/Adjuvant Upfront Chemo"),
          quiet = TRUE)
```
<br>

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
Platin  
```{r Table4 summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
